Dynamic Load Balancing for\\Heterogeneous Systems

### 2011-12-05 paper/paper.tex
Typo

Based on the times shown in the previous figures, it is clear that the
static load balancing is ineffective at improving the overall efficiency
of any of the benchmarks tested.  There were a few scenarios in which
a specific static execution ratio achieved meager speedup (<5\%) over
just the GPU, but these situations were scarce, and did not achieve the
speedup we desired.  Additionally, this small amount of speedup would
require a significant amount of tine-tuning by a programmer.

>>>>

Based on the times shown in the previous figures, it is clear that the
static load balancing is ineffective at improving the overall efficiency
of any of the benchmarks tested.  There were a few scenarios in which
a specific static execution ratio achieved meager speedup ($<$5\%) over
just the GPU, but these situations were scarce, and did not achieve the
speedup we desired.  Additionally, this small amount of speedup would
require a significant amount of tine-tuning by a programmer.
